\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{fontawesome5}
    \usepackage{setspace}
    \usepackage{amssymb}
    \usepackage[hidelinks]{hyperref}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.70in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}
    
\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Siddhesh Surve}}\\
	\vspace{2mm}
	  \href{mailto:paritpranav@gmail.com}{\faEnvelope \ sysurve24@gmail.com} \ \
	  \href{tel:+917058613042}{\faPhone \ +91 8390344586} \ \ \href{https://www.linkedin.com/in/siddheshsurve83/}{\faLinkedin \ Siddhesh Surve} \ \
	  \href{https://github.com/siddheshsurve}{\faGithub \ @siddheshsurve} \\
\end{center}

%==== Education ====%
\header{Education}
\vspace{2mm}
\textbf{Pune Institute of Computer Technology}\hfill Pune, IN\\
Bachelor in Computer Engineering \textit{GPA: 8.66} \hfill Jul 2021 - Jun 2024\\
\vspace{3mm}
\textbf{Dr. Babasaheb Ambedkar Technological University}\hfill Raigad, IN\\
Diploma in Computer Engineering \textit{GPA: 9.80} \hfill Jun 2018 - Jun 2021\\
\vspace{3mm}
\textbf{Sanskar Dham Vidyalaya}\hfill Raigad, IN\\
SSC \textit{Percentage: 89.60} \hfill June 2018\\
\vspace{3mm}

%==== Projects ====%
\header{Projects}
\vspace{2mm}
{\textbf{Helping Hands}}\hfill 
\href{https://github.com/Org-Helping-Hands}{\faGithub}\\
\vspace{1mm}
Tech Stack: React, Node, Express, MYSQL
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
    \item Developed a dynamic web application that works as a middleman between needy people and helpers.
    \item application includes features such as \textbf{uploading posts, searching nearby, requirement filters}, etc.
    \item Developed frontend in \textbf{React JS}, Backend in \textbf{Node JS} and \textbf{Express JS}, \& used \textbf{MYSQL} to manage the database. 
    \item My role included UI/UX designing, frontend development, API integration, and backend development.
\end{itemize}
\vspace{2mm}

{\textbf{MovieVerse}} \hfill \href{https://movieverse-beta.vercel.app/}{\faGlobe[regular]} \
\href{https://github.com/siddheshsurve/movieverse/}{\faGithub}\\
\vspace{1mm}
Tech Stack: React JS, Firebase, Tailwind CSS
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
    \item Developed a Movie Rating application allows to rate and review a movie
    \item For frontend I have used \textbf{React JS} and \textbf{Firebase Firestore} for backend.
    \item I have provided otp based used authentication using \textbf{Firebase Authentication}
\end{itemize}
\vspace{2mm}

{\textbf{ResumePro}} \hfill \href{https://resume-builder-iota-one.vercel.app/}{\faGlobe[regular]} \
\href{https://github.com/siddheshsurve/resume-builder}{\faGithub}\\
\vspace{1mm}
Tech Stack: React JS and CSS
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
    \item Developed an application using \textbf{React JS} that help us to build resume in easy way.
    \item Helps students to get their resume in hand just by  \textbf{filling up a single form} form and app converts into a  \textbf{professional resume.}
    \item Also provides functionality to \textbf{download resume in PDF Format}.
\end{itemize}
\vspace{2mm}

\textbf{Other small scale projects}\hfill  \href{https://github.com/siddheshsurve}{\faGithub}\\
\vspace{1mm}
\begin{itemize} \itemsep 0.5pt
 Youtube Clone, Spotify Clone, Chat App using firebase, Record Keeper, etc.
\vspace{-1mm}

\end{itemize}
\vspace{4mm}



%====Skills ====%

\header{Skills}
\vspace{2mm}
\begin{tabular}{ l l }
        \vspace{2mm}
	\textbf{Programming Languages:} & C++, JavaScript, Java\\ 
        \vspace{2mm}
	\textbf{Web Development:} & Node.js, Express js, HTML, CSS, React\\
        \vspace{2mm}
	\textbf{Databases: } & MySQL, MongoDB, Firestore\\
        \vspace{2mm}
	\textbf{Version Control:} &Git and GitHub \\

\end{tabular}
\vspace{4mm}

%====Skills ====%

\header{CS Fundamentals}
\vspace{2mm}
\begin{tabular}{ l l }
        \vspace{2mm}
	\textbf{OOPS} & \hspace{2cm} \textbf{DBMS}\\ 
        \vspace{2mm}
	\textbf{Operating Systems} & \hspace{2cm} \textbf{Computer Networks}\\
\end{tabular}
\vspace{3mm}

%==== achievements ====%


\header{Achievements}
\vspace{1mm}
\begin{itemize} \itemsep 0.5pt
\item Secured \textbf{Maharashtra state rank 130th} in Diploma batch 2021 among 130000+ students.
\end{itemize}
\vspace{2mm}

\header{Extra Curricular Activities}
\vspace{1mm}
\begin{itemize} \itemsep 0.5pt
\item \textbf{Badminton Singles Finalist} at intra college badminton tournament organized in Dr. Babasaheb Ambedkar Technological University
\end{itemize}


\end{document}